\documentclass[11pt, a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

\begin{center}
    {\Huge Thomas De Grava}\\
    \vspace{0.2cm}
    \href{mailto:thomasdegrava@gmail.com}{thomasdegrava@gmail.com} | 
    \href{https://www.linkedin.com/in/thomasdegrava/}{https://linkedin.com/in/thomasdegrava/} | 
    \href{https://www.github.com/thomas36058}{https://github.com/thomas36058}
\end{center}

\section*{Skills}
\begin{itemize}
    \item Languages: PHP, JavaScript, Typescript
    \item Frameworks and Libraries: React.js, Vue.js, Next.js, Node.js, Laravel, Tailwind CSS, Sage PHP, jQuery
    \item Databases and CMS: WordPress, PostgreSQL, MySQL, MariaDB, Redis
    \item Tools: Git, Figma, CI/CD
\end{itemize}

\section*{Professional Experience}
\subsection*{Studio Visual -- Software Engineer (Fullstack Developer)}\hfill 04/2021 - Present
\begin{itemize}
    \item Developed and implemented innovative web applications with Vue.js and Laravel, enhancing performance.
    \item Led the back-end development with PHP and database interactions.
    \item Developed and maintained custom Wordpress themes using PHP, integrating modern features that improve scalability and user experience.
    \item Enhanced system performance by reviewing and optimizing legacy code, resulting in a 30\% increase in scalability and efficiency
    \item Revamped the front end by addressing bugs and implementing a modern redesign, leading to a 25\% improvement in user satisfaction and engagement.
    \item Sage 9/10 template development
    \item Drove the development of new features, delivering innovative solutions that improve the overall user experience.
    \item Developed custom Gutenberg blocks to enhance website functionality, directly contributing to a 80\% reduction in development time for future pages.
    \item Maintained clear and effective communication with clients, translating their needs into technical requirements, ensuring project alignment with client expectations and achieving high satisfaction rates.
\end{itemize}

\subsection*{Mkt Virtual -- Front End Developer/Project Owner}
\hfill 09/2019 - 05/2021
\begin{itemize}
    \item Developed and supported WordPress themes with Laravel Mix, Javascript and Sass.
    \item Worked closely with UX/UI designers to translate into functional web components.
    \item Provided junior development team leadership, ensuring understanding of requirements, cohesive communication, and meeting deadlines.
\end{itemize}

\subsection*{Bayer Crop Science -- IT Value Capture Intern}
\hfill 01/2018 - 12/2018
\begin{itemize}
    \item Supported staff members in their daily tasks, reduced workload burden and allowed for increased focus on higher priority assignments.
    \item Participated in workshops and presentations related to projects to gain knowledge.  
    \item Improved team efficiency by implementation of Agile and Scrum methodologies for project management.
    \item Facilitated Scrum framework - sprint planning, backlog grooming, daily scrums, sprint reviews, and sprint retrospectives.
\end{itemize}

\section*{Education}
\subsection*{Computer Engineering}
Santa Cecilia University\hfill Bachelor of Science \hfill 01/2015 - 12/2019
\textit{Sao Paulo, Brazil}

\section*{Projects}
\subsection*{Spanty Agency}
\textit Website developed using React, Next.js, Typescript and Tailwind CSS - \href{https://agency-spanty.vercel.app/}{Live}

\subsection*{Dog Control}
\textit Application to control your pet activities, I developed with React, Next.js, Typescript and Tailwind CSS - \href{https://table-application.vercel.app/}{Live}

\subsection*{Space Cargo}
\textit Developed as a freelancer for a transport company. I used the technologies, Wordpress, Sass and Javascript - \href{https://spacecargo.com.br/}{Live}

\end{document}
